Adaptive Waveform Inversion for Transmitted Wave Data

### 2024-11-08 repro/papers/awi/paper.tex
almost there

Asymptotic analysis of AWI and MSWI is based on a family of source
wavelets: for $\lambda > 0$,
\begin{equation}
  \fl(t)= \lambda^{\frac{1}{2}}f_1\left(\frac{t}{\lambda}\right).
\end{equation}
The relation between the dimensionless scale parameter $\lambda$ and
RMS wavelength will be explained below. Correspondingly, denote the
modeling operator with $f=\fl$ by $\Fl$.

@@

\begin{theorem}
  \label{thm:main}
  Assume that Exponential Decay, Single Arrival, and No Return
  hold for $X_{sr} \subset \Omega \times \Omega, M \subset C^{\infty}(\bR^3) \cap L^{\infty}(\bR^3)$.
  Select $r >0$ with units of
  pressure$^2 \times$time$^2$ and $\log \kappa^* \in M$. For $0 <
  \lambda $, set
  $\dl=\Fl[\kappa^*]$ (``noise-free data''), and  define $\ul[\kappa,\dl]$
  to be the solution of 
  equation \ref{eqn:reg} with  $\sigma=r\lambda$, $F=\Fl$ and $d=\dl$..
  There exist $0 < C_* \le C^*$, $0 < C$, and $W: M \times X_{sr}
  \rightarrow \bR^+$ with $C_* \le
  W \le C^*$ so that for
  $\log \kappa \in M$, $(\bx_s,\bx_r) \in X_{sr}$,
  \begin{itemize}
  \item[1. ] $Tu_{\sigma}[\kappa;\dl](\bx_r,\cdot;\bx_s) \in
    L^2(\bR)$;
  \item[2. ] for $\lambda > 0$,
    \begin{equation}
      \label{eqn:mswitt}
      |\|T\ul[\kappa;\dl](\bx_r,\cdot;\bx_s)\|- \lambda^{-\frac{1}{2}} (W[\kappa^*,\kappa](\bx_s,\bx_r))^{\frac{1}{2}}|\tau[\kappa](\bx_s,\bx_r)-\tau[\kappa^*](\bx_s,\bx_r)|| \le C
      \lambda^{\frac{1}{2}};
    \end{equation}
  \item[3. ]for sufficiently small $\lambda$, 
    \begin{equation}
      \label{eqn:awitt}
      \left|\frac{\|T\ul[\kappa;\dl](\bx_r,\cdot;\bx_s)\|}{\|\ul[\kappa,\dl](\bx_r,\cdot;\bx_s)\|}-
        |\tau[\kappa](\bx_s,\bx_r)-\tau[\kappa^*](\bx_s,\bx_r)|\right| \le C \lambda
    \end{equation}
  \end{itemize}
\end{theorem}

@@

Hadamard's construction is local, in both space-time and in the set of
acoustic models. In the present context, it requires the Single
Arrival hypothesis, and for global time validity the No Return
assumption.

\cite{Friedlander:75} produces for each $\log \kappa \in M$ functions $\tau[\kappa]$ (travel time), $a[\kappa]$
(geometric amplitude) on $X_s \times \Omega$ and $b[\kappa]$
(remainder kernel) on $X_s \times \Omega \times \bR$, smooth off the
diagonal - that is, for each $\bx_s \in X_s$, $\tau[\kappa](\bx_s,\cdot) \in C^{\infty}(\Omega \setminus
  \{\bx_s\})$, and similarly for $a[\kappa],b[\kappa]$; The traveltime $\tau$
  satisfies the eikonal equation
  \[
    \sqrt{\frac{\kappa}{\rho}} |\nabla \tau(\bx_s,\cdot)| = 1 \mbox{ in } \Omega \setminus
    \{\bx_s\}, \, \lim_{\bx \rightarrow \bx_s} \tau(\bx_s,\bx) = 0.
  \]
A by-product of the construction is a bound $A>0$ so that for any $\log \kappa \in M$
  and $(\bx_s,\bx_r) \in X_{sr}$,  $|\log a[\kappa](\bx_s,\bx_r)| <
  A$;  With no further assumptionss, there is also a uniform bound on $b(\bx_r,t;\bx_s)$ and
  its derivatives over any finite $t$-interval. However, with the
  addition of the Exponetial Decay assumption, the bound becomes
  global in time: for any $k \ge 0$, there exists $B \ge 0,\delta > 0$ so
  that for any $(\bx_s,\bx_r) \in X_{sr}$, $\log \kappa \in M$, 
\begin{equation}
  |\partial^k_t b[\kappa](\bx_r,t;\bx_r,s)| \le B e^{-\delta t}
  \label{eqn:best}
\end{equation}

@@

Introduce asymptotics in this setting by choosing $w = \wl$
from a family $\{\wl:0 <\lambda \le 1\}$ indexed by the dimensionless parameter
$\lambda$, and defined by
\begin{equation}
  \label{eqn:wfam}
  \wl(t) = \lambda^{-1/2}w_1(t/\lambda).
\end{equation}
The  ``mother wavelet'' $w_1$ is assumed to have properties W1, W2, and
all wavelets $\wl$ in this family
inherit these properties from $w_1$, along with its dimensions
(energy/time$^2$). It follows from these assumptions that the Fourier transform $\fwl$ is
real-valued, even, and real-analytic. The corresponding source waveform $f_{\lambda}$ is
given by
\begin{equation}
  \label{eqn:flambda}
  f_{\lambda}(t) =\frac{1}{\rho} \int_{-\infty}^t\wl =
  \lambda^{1/2}f_1\left(\frac{t}{\lambda}\right).
\end{equation}
Note that for $p \ge 1$,
\begin{equation}
  \label{eqn:lambdanorms}
  \|\wl\|_{L^p(\bR)} = \lambda ^{\frac{1}{p}-\frac{1}{2}}\|w_1\|_{L^p(\bR)},\,\|f_{\lambda}\|_{L^p(\bR)}
  = \lambda ^{\frac{1}{p}+\frac{1}{2}} \|f_1\|_{L^p(\bR)}.
\end{equation}

@@

Note that the AWI objective defined in \ref{eqn:awideforig} and its
modification \ref{eqn:awidef} are actually
squared pulse widths of the adaptive filters $u[\kappa;d]$ and
$u_{\sigma}[\kappa;d]$ respectively.

@@

\subsection{Linking Regularization and Wavelength}
Note that noise-free data $\dl = \Fl[\kappa]$ is bounded in $L^2(X_{sr}
\times \bR)$ uniformly in $\kappa$ and $\lambda$  (Proposition
\ref{eqn:noisefree}, estimates \ref{eqn:Frembd}). 
The minimum value of the right-hand side in equation \ref{eqn:regs} is
the length of the projection of $(\dl,0)^T$ onto the range of
$(\Sl[\kappa[],\sigma I)^T$, so is less than $\|\dl^2\|$.

Suppose conversely that $\Sl[\kappa]\ul[\kappa;d]\| \ge
\frac{1}{2}\|d\|$. Then
\[
  \|d\| \le 2\|\Fl[\kappa]*\ul[\kappa;d] \le
  2\lambda^{\frac{1}{2}}\|\ul[\kappa;d]\|
\]
from Young's inequality, and from the bound \ref{eqn:unorm} this is in
turn
\[
  \le C \frac{\lambda}{\sigma} \|d\|
\]
whence
\[
  \sigma \le C \lambda.
\]
This inequality suggests that in order to expect filtered predicted data
$\Sl[\kappa]\ul[\kappa;d\|$ to remian uniformly (in $\lambda$) close to the data to be
inverted, as the heuristic justification for AWI suggests, the
regularization weight $\sigma$ must be coupled to the wavelength proxy
$\lambda$.  It will be clear from the discussion to follow that choosing $\sigma$ a function of
$\lambda$ roughly proportional to $\lambda$, that is, $C_*\lambda \le
\sigma(\lambda) \le C^*\lambda$ for $C_*,C^*$ satisfying $0 < C_* \le
C^*$, would suffice. The argument is slightly cleaner if $\sigma$ is simply
proportional to (non-dimensional) $\lambda$ by a necessarily
dimensional constant.. Therefore we assume from now on that
\begin{equation}
  \label{eqn:lamsig}
  \sigma = r \lambda
\end{equation}
in which $r$ is a positive constant with dimensions pressure$^2 \times
$ time$^2$.

This choice will eventually be justified by a converse estimate, that
is, showing that under the condition \ref{eqn:lamsig}, the filtered
predicted data $\Sl[\kappa]\ul[\kappa;d]$ has norm at least half that
of $\|\dl\|$ for all $\lambda \in (0,1]$, for properly chosen $r$.

@@

\begin{prop}
  \label{thm:leading}
In the definitions \ref{eqn:mswidef} of $J_{\rm MSWI,\sigma}$ and
\ref{eqn:awidefbis} of $J_{\rm AWI,\sigma}$, set $\sigma = r\lambda$
and replace the data $d$ with
$\dla = \Fla[\kappa^*]$, $S[\kappa]$ with $\Sla[\kappa]$, and $\ul$
with the solution $\uzl$ of the corresponding least squares problem. That is,
\begin{eqnarray}
  \label{eqn:leading}
  \dla & = & \Fla[\kappa^*] = a[\kappa^*]\delta_{\tau[\kappa^*]}*\wl
             \nonumber \\
  \Sla[\kappa]u &=& a[\kappa]\delta_{\tau[\kappa^*]}*\wl *u\nonumber
  \\
  \uzl &=& \mbox{argmin}_{u \in L^2(X_{sr} \times \bR)} (\|\Sla[\kappa]u-\dla\|^2 + r\lambda\|u\|^2)
\end{eqnarray}
%and
%\begin{eqnarray}
%  \label{eqn:awileading}
%  J^0_{\rm MSWI,\lambda}[\kappa;\dla] & = &
%                                         \|T\uzl[\kappa;\dla]\|^2\nonumber\\
%  J^0_{\rm AWI,\lambda}[\kappa;\dla] & = &
%                                       \sum_{(\bx_s,\bx_r) \in X_{sr}} \frac{\|T\uzl[\kappa;\dla](\bx_r,\cdot;\bx_s)\|^2}{\|\uzl[%\kappa;\dla](\bx_r,\cdot;\bx_s)\|^2}
%\end{eqnarray}                 
Then there exists $0 < C_* \le C^*$, $0 < C$, and $W: M \times X_{sr}
\rightarrow \bR^+$ so that for
$\kappa \in M$, $(\bx_s,\bx_r) \in X_{sr}$, $C_* \le
W[\kappa](\bx_s,\bx_r) \le C^*$, and $\uzl$ defined in display
\ref{eqn:leading} for $0 < \lambda \le 1$, 
\begin{equation}
  \label{eqn:mswittz}
 | \|T\uzl[\kappa;\dla] (\bx_r,\cdot;\bx_r)\|^2- 
  \frac{1}{\lambda} W[\kappa](\bx_s,\bx_r) (\tau[\kappa^*]({\bf
  x}_s,{\bf x}_r)-\tau[\kappa]({\bf x}_s,{\bf x}_r))^2 | \le C\lambda,
\end{equation}
and
\begin{equation}
  \label{eqn:awittz}
  \left| \frac{\|T\uzl[\kappa;\dla] (\bx_r,\cdot;\bx_r)\|^2}{
        \|\uzl[\kappa;\dla] (\bx_r,\cdot;\bx_r)\|^2} - (\tau[\kappa^*]({\bf
  x}_s,{\bf x}_r)-\tau[\kappa]({\bf x}_s,{\bf x}_r))^2\right|  \le C\lambda^2.
\end{equation}
m\end{prop}

@@

%It follows that
%\begin{equation}
%  \label{eqn:mswitt}
%  J_{\rm MSWI,\lambda,\lambda}[\kappa;\dla] =
%  \frac{1}{\lambda} \sum_{{\bf x}_s,{\bf x}_r} C[\kappa](\bx_s,\bx_r)(\tau[\kappa^*]({\bf
%  x}_s,{\bf x}_r)-\tau[\kappa]({\bf x}_s,{\bf x}_r))^2 + O(\lambda)
%\end{equation}
%  
%\begin{equation}
%  \label{eqn:awitt}
%J_{\rm AWI,\lambda,\lambda}[\kappa;\dla] = \sum_{{\bf x}_s,{\bf x}_r} (\tau[\kappa^*]({\bf
%  x}_s,{\bf x}_r)-\tau[\kappa]({\bf x}_s,{\bf x}_r))^2 + O(\lambda^2)
%\end{equation}

\noindent {\bf Remark:} Note that the homogeneity in $\lambda$ of the
expressions in equations \ref{eqn:g0} and \ref{eqn:g1} results from
the proportionality between $\lambda$ and the regularization weight in
the definitions \ref{eqn:reg} and \ref{eqn:leading}. Otherwise, such
simple asymptotic relations as the conclusions
of Proposition \ref{thm:leading} would not obtain.

@@

\begin{proof} {\em of Theorem \ref{thm:main}}: From the inequality \ref{eqn:mswittz}
  (suppressing the arguments $\bx_s,\bx_r$),
  \[
   | \|T\uzl[\kappa;\dla] \|- 
   \lambda^{-\frac{1}{2}}
   W[\kappa]^{\frac{1}{2}}|\tau[\kappa^*]-\tau[\kappa]| | \le
   C\lambda^{\frac{1}{2}}
 \]
 Combine with inequality \ref{eqn:difftu} to establish the first
 result \ref{eqn:mswitt}.

>>>>

Asymptotic analysis of AWI and MSWI is based on a family of source
wavelets: for $\lambda > 0$,
\begin{equation}
  \fl(t)= \lambda^{\frac{1}{2}}f_1\left(\frac{t}{\lambda}\right).
\end{equation}
The relation between the dimensionless scale parameter $\lambda$ and
RMS wavelength will be explained below: $\lambda$ may be regarded as a
proxy for wavelength. Correspondingly, denote the
modeling operator with $f=\fl$ by $\Fl$.

@@

\begin{theorem}
  \label{thm:main}
  Assume that Exponential Decay, Single Arrival, and No Return
  hold for $X_{sr} \subset \Omega \times \Omega, M \subset C^{\infty}(\bR^3) \cap L^{\infty}(\bR^3)$.
  Select $\log \kappa^* \in M$. For $0 <
  \lambda \le 1$, set
  $\dl=\Fl[\kappa^*]$ (``noise-free data''), and  define $\ul[\kappa,\dl]$
  to be the solution of 
  equation \ref{eqn:reg} with $F=\Fl$ and $d=\dl$..

  \begin{itemize}
  \item[1. ] $Tu_{\sigma}[\kappa;\dl](\bx_r,\cdot;\bx_s) \in
    L^2(\bR)$;
  \item[2. ] There exist $R_*,R^*,\lambda_*$ with $0<R_*\le R^*, 0 <
    \lambda_*\le 1$ depending on
    $M, X_{sr}$ so that
    \begin{itemize}
    \item[a. ] $\|\Sl[\kappa]\ul[\kappa;\dl]-\dl\| \le
      \frac{1}{2}\|\dl\|$ implies that $\sigma \le R^*\lambda$;
    \item[b. ] $\sigma \le R_*\lambda$ and $\lambda \le \lambda_*$
      implies that $\|\Sl[\kappa]\ul[\kappa;\dl]-\dl\| \le
      \frac{1}{2}\|\dl\|$.
    \end{itemize}
  \end{itemize}
  Choose $r > 0$ and assume that
  \begin{equation}
    \label{eqn:lamsig}
    \sigma = r \lambda.
  \end{equation}.
  Then there exist $0 < C_* \le C^*$, $0 < C$, and $W: M \times X_{sr}
  \rightarrow \bR^+$ with $C_* \le
  W \le C^*$ so that for
  $\log \kappa \in M$, $(\bx_s,\bx_r) \in X_{sr}$,
  \begin{itemize}
  \item[2. ] for $0 <  \lambda \le 1$, 
    \begin{equation}
      \label{eqn:mswitt}
      |\|T\ul[\kappa;\dl](\bx_r,\cdot;\bx_s)\|- \lambda^{-\frac{1}{2}} (W[\kappa^*,\kappa](\bx_s,\bx_r))^{\frac{1}{2}}|\tau[\kappa](\bx_s,\bx_r)-\tau[\kappa^*](\bx_s,\bx_r)|| \le C
      \lambda^{\frac{1}{2}};
    \end{equation}
  \item[3. ]for sufficiently small $\lambda$, 
    \begin{equation}
      \label{eqn:awitt}
      \left|\frac{\|T\ul[\kappa;\dl](\bx_r,\cdot;\bx_s)\|}{\|\ul[\kappa,\dl](\bx_r,\cdot;\bx_s)\|}-
        |\tau[\kappa](\bx_s,\bx_r)-\tau[\kappa^*](\bx_s,\bx_r)|\right| \le C \lambda
    \end{equation}
  \end{itemize}
\end{theorem}
\noindent{\bf Remark:} The heuristic justification for AWI is the possibility of keeping the
filtered predicted data $\Fl[\kappa]*\ul[\kappa;d]$ close to the data
$d$ while updating the bulk modulus $\kappa$. The conclusions 2a and
2b show that for this to be the case, the regularization parameter $\sigma$
must be dominated by the wavelength proxy $\lambda$. This observation underlies the choice
$\sigma = r\lambda$ used in conclusions 3 and 4. A looser relation
would clearly suffice, however the argument lis slightly cleaner if
$\sigma$ is simply held proportional to $\lambda$ as $\lambda
\rightarrow 0$. Note that the units of $r$ and $\sigma$ are pressure$^2 \times$time$^2$.

@@

Hadamard's decomposition is local, in both space-time and in the set of
acoustic models. In the present context, it requires the Single
Arrival hypothesis, and for global time validity the No Return
assumption.

The construction described by \cite{Friedlander:75} produces for each $\log \kappa \in M$ functions $\tau[\kappa]$ (travel time), $a[\kappa]$
(geometric amplitude) on $X_s \times \Omega$ and $b[\kappa]$
(remainder kernel) on $X_s \times \Omega \times \bR$, smooth off the
diagonal - that is, for each $\bx_s \in X_s$, $\tau[\kappa](\bx_s,\cdot) \in C^{\infty}(\Omega \setminus
  \{\bx_s\})$, and similarly for $a[\kappa],b[\kappa]$; The traveltime $\tau$
  satisfies the eikonal equation
  \[
    \sqrt{\frac{\kappa}{\rho}} |\nabla \tau(\bx_s,\cdot)| = 1 \mbox{ in } \Omega \setminus
    \{\bx_s\}, \, \lim_{\bx \rightarrow \bx_s} \tau(\bx_s,\bx) = 0.
  \]
A by-product of the construction is a bound $A>0$ so that for any $\log \kappa \in M$
and $(\bx_s,\bx_r) \in X_{sr}$,
\begin{equation}
  \label{eqn:aest}
  |\log a[\kappa](\bx_s,\bx_r)| <  A.
\end{equation}
With no further assumptionss, there is also a uniform bound on
$b(\bx_r,t;\bx_s)$ and
its derivatives over any finite $t$-interval. However, with the
addition of the Exponetial Decay assumption, the bound becomes
global in time: for any $k \ge 0$, there exists $B \ge 0,\delta > 0$
so that for any $(\bx_s,\bx_r) \in X_{sr}$, $\log \kappa \in M$,
\begin{equation}
  |\partial^k_t b[\kappa](\bx_r,t;\bx_r,s)| \le B e^{-\delta t}
  \label{eqn:best}
\end{equation}

@@

Introduce asymptotics in this setting by choosing $w = \wl$
from a family $\{\wl:0 <\lambda \le 1\}$ indexed by the dimensionless parameter
$\lambda$, and defined by
\begin{equation}
  \label{eqn:wfam}
  \wl(t) = \lambda^{-1/2}w_1\left(\frac{t}{\lambda}\right).
\end{equation}
The  ``mother wavelet'' $w_1$ is assumed to have properties W1, W2, and
all wavelets $\wl$ in this family
inherit these properties from $w_1$, along with its dimensions
(energy/time$^2$). It follows from these assumptions that the Fourier transform $\fwl$ is
real-valued, even, and real-analytic. The corresponding source waveform $f_{\lambda}$ is
given by
\begin{equation}
  \label{eqn:flambda}
  f_{\lambda}(t) =\frac{1}{\rho} \int_{-\infty}^t\wl =
  \lambda^{1/2}f_1\left(\frac{t}{\lambda}\right).
\end{equation}
Note that for $p \ge 1$,
\begin{equation}
  \label{eqn:lambdanorms}
  \|\wl\|_{L^p(\bR)} = \lambda ^{\frac{1}{p}-\frac{1}{2}}\|w_1\|_{L^p(\bR)},\,\|f_{\lambda}\|_{L^p(\bR)}
  = \lambda ^{\frac{1}{p}+\frac{1}{2}} \|f_1\|_{L^p(\bR)}.
\end{equation}

@@

Note that the AWI objective defined in \ref{eqn:awidefmain} is actually
squared pulse width of the adaptive filter 
$u_{\sigma}[\kappa;d]$ respectively.

@@

\subsection{Linking Regularization and Wavelength}
Note that noise-free data $\dl = \Fl[\kappa]$ is bounded in $L^2(X_{sr}
\times \bR)$ uniformly in $\kappa$ and $\lambda$  (Proposition
\ref{thm:noisefree}, estimates \ref{eqn:Frembd}). 
The minimum value of the right-hand side in equation \ref{eqn:regs} is
the length of the projection of $(\dl,0)^T$ onto the range of
$(\Sl[\kappa[],\sigma I)^T$, so is less than $\|\dl^2\|$.

Suppose conversely that $\|\Sl[\kappa]\ul[\kappa;d] - \dl\| \le
\frac{1}{2}\|d\|$. Then $\|\Sl[\kappa]\ul[\kappa;d] \| \ge
\frac{1}{2}\|d\|$, so
\[
  \|d\| \le 2\|\Fl[\kappa]*\ul[\kappa;d] \le
  2\lambda^{\frac{1}{2}}\|\ul[\kappa;d]\|
\]
from Young's inequality, Proposition \ref{thm:noisefree}, and
inequalities \ref{\eqn:lambdanorms}. From the bound \ref{eqn:unorm} this is in
turn
\[
  \le R^* \frac{\lambda}{\sigma} \|d\|
\]
whence
\[
  \sigma \le R^* \lambda.
\]
for a suitable $R^*>0$ independent of $\log \kappa \in M$ and $\lambda
\in (0,1]$. This establishes conclusion 2a in Theorem \ref{thm:main}, and
suggests that in order to expect filtered predicted data
$\Sl[\kappa]\ul[\kappa;d\|$ to remian uniformly (in $\lambda$) close to the data to be
inverted, as the heuristic justification for AWI suggests, the
regularization weight $\sigma$ must be coupled to the wavelength proxy
$\lambda$. Therefore we assume from now on that equation
\ref{eqn:lamsig} holds,  
in which $r$ is a positive constant with dimensions pressure$^2 \times 
$ time$^2$.

@@

\begin{prop}
  \label{thm:leading}
In the definitions \ref{eqn:mswidefmain} of $J_{\rm MSWI,\sigma}$ and
\ref{eqn:awidefmain} of $J_{\rm AWI,\sigma}$, set $\sigma = r\lambda$
(equation \ref{eqn:lamsig}
and replace the data $d$ with
$\dla = \Fla[\kappa^*]$, $S[\kappa]$ with $\Sla[\kappa]$, and $\ul$
with the solution $\uzl$ of the corresponding least squares problem. That is,
\begin{eqnarray}
  \label{eqn:leading}
  \dla & = & \Fla[\kappa^*] = a[\kappa^*]\delta_{\tau[\kappa^*]}*\wl
             \nonumber \\
  \Sla[\kappa]u &=& a[\kappa]\delta_{\tau[\kappa^*]}*\wl *u\nonumber
  \\
  \uzl &=& \mbox{argmin}_{u \in L^2(X_{sr} \times \bR)} (\|\Sla[\kappa]u-\dla\|^2 + r\lambda\|u\|^2)
\end{eqnarray}
%and
%\begin{eqnarray}
%  \label{eqn:awileading}
%  J^0_{\rm MSWI,\lambda}[\kappa;\dla] & = &
%                                         \|T\uzl[\kappa;\dla]\|^2\nonumber\\
%  J^0_{\rm AWI,\lambda}[\kappa;\dla] & = &
%                                       \sum_{(\bx_s,\bx_r) \in X_{sr}} \frac{\|T\uzl[\kappa;\dla](\bx_r,\cdot;\bx_s)\|^2}{\|\uzl[%\kappa;\dla](\bx_r,\cdot;\bx_s)\|^2}
%\end{eqnarray}                 
Then there exists $0 < C_* \le C^*$, $0 < C$, and $W: M \times X_{sr}
\rightarrow \bR^+$ so that for
$\kappa \in M$, $(\bx_s,\bx_r) \in X_{sr}$, $C_* \le
W[\kappa](\bx_s,\bx_r) \le C^*$, and $\uzl$ defined in display
\ref{eqn:leading} for $0 < \lambda \le 1$, 
\begin{equation}
  \label{eqn:mswittz}
 | \|T\uzl[\kappa;\dla] (\bx_r,\cdot;\bx_r)\|^2- 
  \frac{1}{\lambda} W[\kappa](\bx_s,\bx_r) (\tau[\kappa^*]({\bf
  x}_s,{\bf x}_r)-\tau[\kappa]({\bf x}_s,{\bf x}_r))^2 | \le C\lambda,
\end{equation}
and
\begin{equation}
  \label{eqn:awittz}
  \left| \frac{\|T\uzl[\kappa;\dla] (\bx_r,\cdot;\bx_r)\|^2}{
        \|\uzl[\kappa;\dla] (\bx_r,\cdot;\bx_r)\|^2} - (\tau[\kappa^*](\bx_s,\bx_r)-\tau[\kappa]({\bf x}_s,{\bf x}_r))^2\right|  \le C\lambda^2.
\end{equation}
Finally, for $\sigma = r\lambda$ with $r$ sufficiently small,
\begin{equation}
  \label{eqn:Sutz}
  \Sla[\kappa]\uzl[\kappa;\dzl] \ge \frac{1}{2}\|\dzl\|
\end{equation}
\end{prop}

@@

Similar reasoning establishes the inequality \ref{eqn:Sutz}:
\[
  \Sla[\kappa]\uzl[\kappa;\dla](\omega) = a^* \wl(\omega) \left(\frac{|\wl(\omega)|^2}{|\wl(\omega)|^2
      + \frac{\sigma}{a^2}}\right)
\]
\[
  = a^* \lambda^{\frac{1}{2}}w_1(\lambda \omega) \left(\frac{a^2|w_1(\lambda\omega)|^2}{a^2|w_1(\lambda\omega)|^2
      + \frac{\sigma}{\lambda}}\right),
\]
so
\[
  \|\Sla[\kappa]\uzl[\kappa;\dla]\|^2 = \left(\frac{a*}{a}\right)^2
  \int a^2|w_1|^2\left(\frac{a^2|w_1|^2}{a^2|w_1|^2 +
      \frac{\sigma}{\lambda}}\right)^2 \ge \frac{\lambda}{\sigma}
  (a^*)^2a^2 \int |w_1|^4 
\]
By virtue of the bound \ref{eqn:aest}, $(a^*)^2a^2 \int |w_1|^4$ is bounded below
by a positive constant independent of $\log \kappa \in M,
(\bx_s,\bx_r) \in X_{sr}$. Since $\dl$ is bounded above by a similar
constant, conclude if $r = \sigma/\lambda$ is sufficiently small, the
inequality \ref{eqn:Sutz} holds.
\end{proof}

\noindent {\bf Remark:} Inequality \ref{eqn:Sutz} is the converse
promised earlier to the observation that requiring the filtered
predicted data $\Sl[\kappa]u_{\sigma}[\kappa;\dl]$, hence the filtered
data residual, to be comparable in norm to the data $d$ implied that
$\sigma$ should be dominated by $\lambda$, as the relation
$\sigma=r\lambda$ ensures. Of course, this is an analogue, with $\Sl$
replaced by its leading approximation $\Sla$, and $\dl$ replaced by $\dla$.

@@

\begin{proof} {\em of Theorem \ref{thm:main}}:
Conclusions 1 and 2a have already been established. Conclusion 2b
follows from equation \ref{eqn:Sutz} in Proposition \ref{thm:leading},
combined with the first estimate in \ref{eqn:remest} and the bounds
\ref{eqn:Srembd}.

  From the inequality \ref{eqn:mswittz}
  (suppressing the arguments $\bx_s,\bx_r$),
  \[
   | \|T\uzl[\kappa;\dla] \|- 
   \lambda^{-\frac{1}{2}}
   W[\kappa]^{\frac{1}{2}}|\tau[\kappa^*]-\tau[\kappa]| | \le
   C\lambda^{\frac{1}{2}}
 \]
 Combine with inequality \ref{eqn:difftu} to establish the first
 result \ref{eqn:mswitt}.
